---
title: "Weight of Fish"
author: "Sarah Medina"
date: "11/01/2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight


## Perch  

```{r}
Fish <- read.csv(file= "Fish.csv")

Perch <- filter(Fish, Species == "Perch")

Perch <- select(Perch, -Species)
```


### Best Models

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

This chart indicates that the best regression model is the one above the two. Height and weight has the highest Adjusted R 2 value at 0.9400. The second best regression model with the highest adjusted R 2 value is the one above the 3 it is at 0.9390. 
## Bream  

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements